Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-05-13 paper.qmd
Addresses

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
author:
  - name: Graham Farrell
    affiliations:
      - name: University of Leeds
        address: School of Law, University of Leeds, Leeds, UK
        orcid: 0000-0002-3987-8457
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: 0000-0001-5679-6536
  - name: Steve O'Hern
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
        orcid: tbc
keywords: 
  - Cycling
  - Hotspots 
  - Road Safety
  - Active Travel
  - Transport Planning
  - Near Misses
date: last-modified
format:
  # pdf: default
  arxiv-pdf:
    keep-tex: true
linenumbers: true # Add (continuous) line numbers?
doublespacing: true # Double space the PDF output?
runninghead: "Preprint" # The text on the top of each page of the output
authorcols: false # Should authors be listed in a single column (default) or in multiple columns (`authorcols: true`)
---

>>>>

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
author:
  - name: Graham Farrell
    corresponding: true
    affiliations:
      - name: University of Leeds
        department: School of Law
        address: The Liberty Building
        city: Leeds
        country: United Kingdom
        postal-code: LS2 9JT
    orcid: 0000-0002-3987-8457
  - name: Robin Lovelace
    affiliations:
      - name: University of Leeds
        department: Institute for Transport Studies
        address: University Road
        city: Leeds
        country: United Kingdom
        postal-code: LS2 9JT
      - name: Active Travel England
        # department: Data and Digital
        # address: West Offices Station Rise
        # city: York
        # country: United Kingdom
        # postal-code: YO1 6GA
    orcid: 0000-0001-5679-6536
  - name: Steve O'Hern
    affiliations:
      - name: University of Leeds
        department: Institute for Transport Studies
        address: University Road
        city: Leeds
        country: United Kingdom
        postal-code: LS2 9JT
      - name: Monash University Accident Research Centre
        address: Clayton, VIC 3800, Australia
    orcid: 0000-0002-7961-3875
keywords: 
  - Cycling
  - Hotspots 
  - Road Safety
  - Active Travel
  - Transport Planning
  - Near Misses
date: last-modified
format:
  # pdf: default
  arxiv-pdf:
    keep-tex: true
linenumbers: true # Add (continuous) line numbers?
doublespacing: false # Double space the PDF output?
runninghead: "Preprint" # The text on the top of each page of the output
authorcols: false # Should authors be listed in a single column (default) or in multiple columns (`authorcols: true`)
---
